Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-05-29 analysis/paper/London_HauloutBehavior.Rmd
remove early references to Fig 7 and Fig 9

Age and sex class were not included in the model for bearded seals due to our
lower sample size for adult and young-of-year age classes. As such, results are
shown for all ages (Figure \@ref(fig:beardedHOCal); see also
\@ref(fig:beardedPredSE)). Additionally, after approximately 9 months, 7 devices
deployed on the rear flipper of bearded seals reported implausible hourly
percent-dry data (100% dry for several weeks but indicative of movement and
increasing transmission rates (see Boveng & Cameron [-@boveng2013])). All data after the first
instance of unrealistic values were censored from this analysis. In addition to
a peak around local solar noon, the bearded seal model predicted additional
haul-out activity around local midnight. In concert with the lower magnitude of
haul-out probability, bearded seal haul-out behavior was also more protracted
throughout the spring season compared to ribbon (Figure \@ref(fig:ribbonHOCal))
and spotted seals (Figure \@ref(fig:spottedHOCal)). Overall, bearded seals were
less likely to haul out and had a bi-modal distribution of haul-out probability
across the day.

>>>>

Age and sex class were not included in the model for bearded seals due to our
lower sample size for adult and young-of-year age classes. As such, results are
shown for all ages (Figure \@ref(fig:beardedHOCal); see also
\@ref(fig:beardedPredSE)). Additionally, after approximately 9 months, 7 devices
deployed on the rear flipper of bearded seals reported implausible hourly
percent-dry data (100% dry for several weeks but indicative of movement and
increasing transmission rates (see Boveng & Cameron [-@boveng2013])). All data after the first
instance of unrealistic values were censored from this analysis. In addition to
a peak around local solar noon, the bearded seal model predicted additional
haul-out activity around local midnight. In concert with the lower magnitude of
haul-out probability, bearded seal haul-out behavior was also more protracted
throughout the spring season compared to ribbon
and spotted seals (see below). Overall, bearded seals were
less likely to haul out and had a bi-modal distribution of haul-out probability
across the day.
